Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-19 WSSSPE2_report/WSSSPE2_review.tex
Section 11: minor changes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions} \label{sec:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo{currently just pre-workshop stuff - needs to be updated}

@@

@@

WSSSPE has developed an engaging online mechanism via the online social network
Twitter (hashtag ``\#WSSSPE''). There were substantially more tweets during
WSSSPE2 than WSSSPE1 or WSSSPE1.1. The WSSSPE community counts 178 tweets and
61 folllowers between May 16, 2013 to April 18, 2015. Some tweets were re-tweeeted or like more than the others.
Table~\ref{tab:tweets} summarizes the top posts and their statistics.

 \begin{table*}[t]
 \centering
\caption{Top tweets tagged \#WSSSPE on Nov 16, 2014.}\label{tab:tweets}
  \begin{scriptsize}
  \begin{tabular}{l|l|r|r}
 \hline
    Source &   Tweet  & Retweets &  Favorites
\\ \hline 
% Software Carpentry & Nov 17 & You call it ``project planning'' if it hasn't started yet,          & 8 & 1
%\\                          & &  and``software sustainability'' if it has and wasn't planned.     &    & 
%
% Neil P Chue Hong   &  Here's @SoftwareSaved guidance on Writing and using a software & 7 & 1
%\\     &  management plan used by EPSRC software grants    &    &  
% \\     &  http://w%ww.software.ac.uk/resources/guides/software-management-plans  &    & 
%
 Neil P Chue Hong  &  @jameshowison as well as software plans   & 4 & 7
\\   &   http://www.software.ac.uk/resources/guides/software-management-plans &    & 
\\   &   we provide a software evaluation tool:   &    & 
\\   &   http://www.software.ac.uk/online-sustainability-evaluation  &    & 
%
\\ Dr Tom Crick  & $56\%$ of UK researchers develop their own software $\rightarrow  140,000$   &  14 & 8
\\ & UK researchers write research software w$/$out any formal training &    & 
%
\\ Karthik Ram  &  ``Institutionalize metadata before metadata institutionalizes you'' & 8 & 6
%
\\ Josh Greenberg  &  ``1. retract any paper with bitrotten dependencies'' *mic drop* & 13 & 8
\\   &   ``2. add anyone who fixes bitrot as an author'' *mic drop*  &    & 
%
\\ Ethan White &  ``@rOpenSci is all about community... our measures of success  & 9 & 3
\\ &   [include] how many faces are up on our community page''   &    & 
%
\\ Ethan White & Daniel Katz talking about implementing transitive credit for  & 9 & 7
\\ &  software http://arxiv.org/abs/1407.5117  Work with @arfon  &    & 
% 
%\\ Aleksandra Pawlik  &  ``Tell us how you test your scientific software'' @gvwilson @swcarpentry  & 7 & 2
% 
%\\ Aleksandra Pawlik  & Lack of training as one of the main barriers for sustainable software & 7 & 2
%\\ &    at @Supercomputing. @swcarpentry @datacarpentry can fix that!  & & 
%
\\ Kaitlin Thaney  & My slides from this morning's keynote at & 11 & 12
\\ &  WSSSPE on Designing for Truth, Scale $+$ Sustainability:  & & 
\\ &   http://www.slideshare.net/kaythaney/     & & 
\\ &  designing-for-truth-scale-and-sustainability-wssspe2-keynote   & & 
%
\\ Neil P Chue Hong & @kaythaney shout out for @swcarpentry @datacarpentry & 9 & 4
\\ &  @rOpenSci @stilettofiend around open training activities for sustainability  & & 
%
%\\ Richard Littauer &  Sweet! @swcarpentry has had 4000+ learners in the past year. & 6 & 
%
\\ Neil P Chue Hong & For those interested in Github - Figshare/Zenodo integration, & 5 & 12
\\ & but want SWORD/DSpace/Fedora/ePrints see:  & & 
\\ & http://blog.stuartlewis.com/2014/09/09/github-to-repository-deposit/  & & 
%
\\ Hilmar Lapp & Re: adopting the unix philosophy, consider signing the Small Tools in & 7 & 6
\\ & Bioinformatics Manifesto: https://github.com/pjotrp/bioinformatics   & 
%
\\Andre Luckow &  ``Traditions last not because they are excellent, & 12 & 3 
\\ & but because influential people are averse to change...''  C. Sunstein     & & 
% 
\\ Dr Tom Crick &  ``Can I Implement Your Algorithm?'':  A Model for  Reproducible & 9 & 8
\\   &  Research Software http://arxiv.org/abs/1407.5981  & & 
%
\\Mozilla Science Lab & At a loose end this Sunday? Care about reproducibility, software  $+$ & 10 & 5
\\ &  \#openscience? Follow the    \#WSSSPE hashtag for more, live from New Orleans.  &  &
%
\\Kaitlin Thaney & I'm in New Orleans at \#WSSSPE , speaking at 9:50 ET on  scientific software & 9 & 9
\\ &   $+$ sustainability. Tune in! Live stream: http://ustre.am/17ddh & & 
%
\\   Daniel S. Katz & \#WSSSPE Agenda (Sunday):  & 10 & 1
\\ & http://wssspe.researchcomputing.org.uk/wssspe2/agenda/   &  &
\\ & URL for live stream of keynotes \& lightning talks: http://ustre.am/17ddh   &  &
\\ \hline
    \end{tabular}
    \end{scriptsize}
\end{table*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions} \label{sec:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo{currently just pre-workshop stuff - needs to be updated}

@@

\begin{table*}[t]
\centering
\caption{Top tweets tagged \#WSSSPE on Nov 16, 2014.}\label{tab:tweets}
  \begin{scriptsize}
  \begin{tabular}{l|l|r|r}
 \hline
    Author  &   Tweet  & Retweets &  Favorites
\\ \hline 
% Software Carpentry & Nov 17 & You call it ``project planning'' if it hasn't started yet,          & 8 & 1
%\\                          & &  and``software sustainability'' if it has and wasn't planned.     &    & 
%
% Neil P Chue Hong   &  Here's @SoftwareSaved guidance on Writing and using a software & 7 & 1
%\\     &  management plan used by EPSRC software grants    &    &  
% \\     &  http://w%ww.software.ac.uk/resources/guides/software-management-plans  &    & 
%
 Neil P Chue Hong  &  @jameshowison as well as software plans   & 4 & 7
\\   &   http://www.software.ac.uk/resources/guides/software-management-plans &    & 
\\   &   we provide a software evaluation tool:   &    & 
\\   &   http://www.software.ac.uk/online-sustainability-evaluation  &    & 
%
\\ Dr Tom Crick  & $56\%$ of UK researchers develop their own software $\rightarrow  140,000$   &  14 & 8
\\ & UK researchers write research software w$/$out any formal training &    & 
%
\\ Karthik Ram  &  ``Institutionalize metadata before metadata institutionalizes you'' & 8 & 6
%
\\ Josh Greenberg  &  ``1. retract any paper with bitrotten dependencies'' *mic drop* & 13 & 8
\\   &   ``2. add anyone who fixes bitrot as an author'' *mic drop*  &    & 
%
\\ Ethan White &  ``@rOpenSci is all about community... our measures of success  & 9 & 3
\\ &   [include] how many faces are up on our community page''   &    & 
%
\\ Ethan White & Daniel Katz talking about implementing transitive credit for  & 9 & 7
\\ &  software http://arxiv.org/abs/1407.5117  Work with @arfon  &    & 
% 
%\\ Aleksandra Pawlik  &  ``Tell us how you test your scientific software'' @gvwilson @swcarpentry  & 7 & 2
% 
\\ Aleksandra Pawlik  & Lack of training as one of the main barriers for sustainable software & 10 & 4
\\ &    at @Supercomputing. @swcarpentry @datacarpentry can fix that!  & & 
%
\\ Kaitlin Thaney  & My slides from this morning's keynote at & 11 & 12
\\ &  WSSSPE on Designing for Truth, Scale $+$ Sustainability:  & & 
\\ &   http://www.slideshare.net/kaythaney/     & & 
\\ &  designing-for-truth-scale-and-sustainability-wssspe2-keynote   & & 
%
\\ Neil P Chue Hong & @kaythaney shout out for @swcarpentry @datacarpentry & 9 & 4
\\ &  @rOpenSci @stilettofiend around open training activities for sustainability  & & 
%
%\\ Richard Littauer &  Sweet! @swcarpentry has had 4000+ learners in the past year. & 6 & 
%
\\ Neil P Chue Hong & For those interested in Github - Figshare/Zenodo integration, & 5 & 12
\\ & but want SWORD/DSpace/Fedora/ePrints see:  & & 
\\ & http://blog.stuartlewis.com/2014/09/09/github-to-repository-deposit/  & & 
%
\\ Hilmar Lapp & Re: adopting the unix philosophy, consider signing the Small Tools in & 7 & 6
\\ & Bioinformatics Manifesto: https://github.com/pjotrp/bioinformatics   & 
%
\\Andre Luckow &  ``Traditions last not because they are excellent, & 12 & 3 
\\ & but because influential people are averse to change...''  C. Sunstein     & & 
% 
\\ Dr Tom Crick &  ``Can I Implement Your Algorithm?'':  A Model for  Reproducible & 9 & 8
\\   &  Research Software http://arxiv.org/abs/1407.5981  & & 
%
\\Mozilla Science Lab & At a loose end this Sunday? Care about reproducibility, software  $+$ & 10 & 5
\\ &  \#openscience? Follow the    \#WSSSPE hashtag for more, live from New Orleans.  &  &
%
\\Kaitlin Thaney & I'm in New Orleans at \#WSSSPE , speaking at 9:50 ET on  scientific software & 9 & 9
\\ &   $+$ sustainability. Tune in! Live stream: http://ustre.am/17ddh & & 
%
\\   Daniel S. Katz & \#WSSSPE Agenda (Sunday):  & 10 & 1
\\ & http://wssspe.researchcomputing.org.uk/wssspe2/agenda/   &  &
\\ & URL for live stream of keynotes \& lightning talks: http://ustre.am/17ddh   &  &
\\ \hline
    \end{tabular}
    \end{scriptsize}
\end{table*}

@@

WSSSPE has developed an engaging online mechanism via the online social network
Twitter (hashtag ``\#WSSSPE''). There were substantially more tweets (messages) during
WSSSPE2 than WSSSPE1 or WSSSPE1.1. The WSSSPE community counts 178 tweets and
61 followers between May 16, 2013 and April 18, 2015. Some tweets were re-tweeeted or liked more than the others.
Table~\ref{tab:tweets} summarizes the top tweets and their statistics on the day of workshop, Nov 16, 2014,
reverberating some of the main points and highlights in the meeting.
